On Optimality of Finite Element Integration

### 2015-10-25 TOMS_Paper/assembly.tex
Other fixes

At this point, three main issues are still to be addressed: 
\begin{itemize}
\item 
\item Given a monomial, deciding whether to apply pre-evaluation (instead of sharing elimination). Recall from Section~\ref{sec:pre-evaluation} that pre-evaluation can actually increase the operation count because of product expansion. In the following, by saying that pre-evaluation is profitable, we simply mean that the resulting operation count is smaller than that produced through sharing elimination.
\item Consider a form comprising two monomials $m1$ and $m2$. Assume that pre-evaluation is profitable for $m1$ but not for $m2$, and that $m1$ and $m2$ share at least one term (e.g. some basis functions). If pre-evaluation were applied to $m1$, sharing between $m1$ and $m2$ would be lost. We then need a mechanism to understand what transformation -- pre-evaluation or sharing elimination -- results in the highest operation count reduction. In other words, we seek a strategy for finding the global optimum. 
\end{itemize}

For the moment, let us assume that we own a cost function $\theta : M \rightarrow \mathbb{Z}$ that, given a monomial $m \in M$, returns the number of operations saved or introduced if pre-evaluation were applied to $m$. $\theta(m) < 0$ indicates that pre-evaluation is not profitable, because the operation count would actually increase by $|\theta(m)|$. Analogous considerations stand for $\theta(m) > 0$. We will show how to construct a proper $\theta$ in Section~\ref{sec:op_count}. Having defined $\theta$, we can now elaborate on the transformation algorithm, for which pseudo-code is provided in Figure~\ref{code:intuition}.

@@

\subsubsection{Profitability of pre-evaluation}
\label{sec:op_count}
We build the cost function $\theta$. According to what established in the previous section, we have $\theta(m) = \theta_{wo}(m) - \theta_{w}(m)$; we recall that $\theta_{wo}$ and $\theta_{w}$ represent the operation counts without and with pre-evaluation. In the following, we explain how to derive these two values.

>>>>

At this point, three main issues are still to be addressed: 
\begin{enumerate}
\item Given a monomial, deciding whether to apply pre-evaluation (instead of sharing elimination). Recall from Section~\ref{sec:pre-evaluation} that pre-evaluation can actually increase the operation count because of product expansion. In the following, by saying that pre-evaluation is profitable, we simply mean that the resulting operation count is smaller than that produced through sharing elimination.
\item 
\item Consider a form comprising two monomials $m1$ and $m2$. Assume that pre-evaluation is profitable for $m1$ but not for $m2$, and that $m1$ and $m2$ share at least one term (e.g. some basis functions). If pre-evaluation were applied to $m1$, sharing between $m1$ and $m2$ would be lost. We then need a mechanism to understand what transformation -- pre-evaluation or sharing elimination -- results in the highest operation count reduction. In other words, we seek a strategy for finding the global optimum. 
\end{enumerate}

For the moment, let us assume that we own a cost function $\theta : M \rightarrow \mathbb{Z}$ that, given a monomial $m \in M$, returns the gain/loss of pre-evaluating $m$ in place of sharing elimination. $\theta(m) < 0$ indicates that pre-evaluation is not profitable, with the operation count increasing by $|\theta(m)|$. Similarly for $\theta(m) > 0$. We return to the issue of constructing $\theta$ in Section~\ref{sec:op_count}. Having defined $\theta$, we now show the algorithm driving the transformation process. The pseudo-code is provided in Figure~\ref{code:intuition}.

@@

\subsubsection{Profitability of pre-evaluation}
\label{sec:op_count}

%TODO : say that avoiding useless pre-evaluation is extremely important !!!!!!!!!!! Performing sharing elimination is fast and easy, pre-evaluationi s not !

We build the cost function $\theta$. According to what established in the previous section, we have $\theta(m) = \theta_{wo}(m) - \theta_{w}(m)$; we recall that $\theta_{wo}$ and $\theta_{w}$ represent the operation counts without and with pre-evaluation. In the following, we explain how to derive these two values.
